Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2023-01-16 paper/manuscript.Rmd
reflected comments on intro
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

To address this question, we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on learners' skill level. In our previous research [@tominaga_2022], we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question of whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

>>>>

To address this question, we investigated whether and how experts can exaggerate specific parameters of the action to be acquired depending on learners' skill level. We chose to study expressive music performance, in which experts need to modulate multiple performance parameters such as articulation and dynamics to implement expression [@cancino-chacon_2018]. Musicians can create their unique expression and interpretation of music even if they play exactly the same piece because when and how they change multiple performance parameters are different. By studying expressive performance, we can investigate how precisely experts can highlight specific parameters in a multidimentional space of expression (e.g., tempo, articulation dynamics) depending on the goal of teaching (e.g., to teach articulation or dynamics) even when they are performing the same piece.

In our previous research [@tominaga_2022], we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, experts were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question of whether experts would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If experts modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired. For example, if learners did not implement notated articulation during their performance, experts should exaggerate the performance relevant to articulation. However, if learners implemented notated articulation correctly, experts should not exaggerate the performance relevant to articulation.

### 2023-01-16 paper/manuscript.tex
reflected comments on intro
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

To address this question, we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on learners' skill level. In our previous research (Tominaga, Knoblich, \& Sebanz, 2022), we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question of whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

@@

>>>>

To address this question, we investigated whether and how experts can exaggerate specific parameters of the action to be acquired depending on learners' skill level. We chose to study expressive music performance, in which experts need to modulate multiple performance parameters such as articulation and dynamics to implement expression (Cancino-Chacón, Grachten, Goebl, \& Widmer, 2018). Musicians can create their unique expression and interpretation of music even if they play exactly the same piece because when and how they change multiple performance parameters are different. By studying expressive performance, we can investigate how precisely experts can highlight specific parameters in a multidimentional space of expression (e.g., tempo, articulation dynamics) depending on the goal of teaching (e.g., to teach articulation or dynamics) even when they are performing the same piece.

In our previous research (Tominaga, Knoblich, \& Sebanz, 2022), we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, experts were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question of whether experts would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If experts modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired. For example, if learners did not implement notated articulation during their performance, experts should exaggerate the performance relevant to articulation. However, if learners implemented notated articulation correctly, experts should not exaggerate the performance relevant to articulation.

@@

\leavevmode\vadjust pre{\hypertarget{ref-cancino-chacon_2018}{}}%
Cancino-Chacón, C. E., Grachten, M., Goebl, W., \& Widmer, G. (2018). Computational {Models} of {Expressive Music Performance}: {A Comprehensive} and {Critical Review}. \emph{Frontiers in Digital Humanities}, \emph{5}.
